In the preceding years a new level of abstraction in development have been
evolving. Utilizing a higher level of abstraction, than high-level programming
languages, we have Model Driven Development. This new paradigm is combining a
focus on automation and code generation, to enable a new way of black boxing
solutions within a multitude of specialists outside traditional programming
while securing platform independency.

In this paper, we will propose a new code generator for the ECDAR tool (see
Sec. \ref{introduction-ecdar}. Until now, there exists no such generator. We
will outline our approach in detail and also look at related work to this
topic. While there already exists a code generator for a tool very similar to
ECDAR. However, ECDAR includes some features which make it incompatible with
these generators. The code we generate is executable in a simulator environment
and serves as a starting point for developing an embedded system.

\subsection {Real Time Computing}
\label{introduction-rts}

Real-time computing is the study of hardware and software systems that must
satisfy explicit response-time constraints or risk severe consequences,
including failure. Timed systems are used in a wide range of domains including
communications, embedded systems, real-time and automated control.  They can be
easily found in our environment; one of simple examples is the airbag system in
a car.  The real-time constraint in this system is the reaction time between
crash sensors receiving input and the deployment of airbags. Among some of the
important characteristics of real-time systems we can distinguish extreme
reliability and safety as they are very often safety-critical.

\subsection{ECDAR}
\label{introduction-ecdar}

The ``Environment for Compositional Design and Analysis of Real Time Systems''
(ECDAR) - is a graphical tool based on UPPAAL TIGA
\cite{behrmann_uppaal-tiga:_2006} that allows to visually create models of
real-time systems. Unlike UPPAAL \cite{larsen_uppaal_1997}, it is implementing a
complete specification theory for real time systems
\cite{David:2010:TIA:1755952.1755967,conf/atva/DavidLLNW10}. In ECDAR,
components of the system are described as automatons extended with clocks (timed
automata), that can be combined to form larger comprehensive system
descriptions. Correct specification of composition is supported by well defined
compositional reasoning theory, consisting of operators like: parallel
composition, conjunction, satisfaction checking and refinement. On the top of
that, the tool allows for scalable verification of models by querying the
implementation with verification questions \cite{conf/atva/DavidLLNW10}.


\subsection{Project}
\label{introduction-problemfield}
This paper will follow an implementation of code generation from ECDAR to
Java. The proposed implementation of the ECDAR code generator is split up in two
parts. The first part is a framework of abstract classes, implementing in as
much detail as possible the single elements used in ECDAR specifications. The
second is the actual code generation. Our code generator generates sources which
inherit from the abstract framework to minimize the amount of code that needs
actually to be generated. The paper will also detail the different testing
issues and benefits of implementing code generation for ECDAR.

To write programs that meet the demands of real-time systems in Java the
Real-Time Specification for Java (RTSJ) is needed. RTSJ is a set of interfaces
and behavioral specifications that allow for real-time programming in the Java
programming language.  Real-time in the RTSJ context means ``the ability to
reliably and predictably respond to a real-world
event''\footnote{\url{http://www.oracle.com/technetwork/java/javase/tech/index-jsp-139921.html#what}}.
So ``real-time'' is about predictable timing. In our implementation we don't
utilize RTSJ, so we can't currently guarantee thread prioritization and
timing. RTSJ is only commercially available but can be integrated in to our
framework in the future.
