The proposed implementation of the ECDAR code generator is split up
in two parts. The first part is a framework of abstract classes, implementing
in as much detail as possible the single parts of ECDAR specifications
(i.e. edges, locations, TIOA). The second is the actual code generation.
Our code generator generates source code which inherit from the abstract
framework to minimize the amount of code that needs to be
generated. This means that nearly all design decisions have been made
prior to generating code, reducing space for possible errors. This
section describes our implemented subset of ECDAR and the code generator
in detail.

\subsection{Tasks}
\label{subsec:tasks}

ECDAR defines the behavior of a system as a state machine. This behavior
is, however, still too abstract to justify code generation. We can
generate code which implements the behavior of state machines, but
in essence, the system would then only produce messages.

To make this tool more useful, we introduce the notion of tasks as an extension
to the language. Each location is assigned exactly one task. A task is a
procedure which will be executed as soon as an automaton traverses over an edge,
arriving at a new location. Such a task could for example be a procedure that
heats up the water in the coffe machine from Fig. \ref{bev-machine} or some code
that extends the undercarriage of a plane when approaching the landing strip.

Tasks can either be preemptive or non-preemptive. This property becomes
important for defining behavior of automata when they are notified
about input by the controller.

ECDAR is input-enabled (see Sect. \ref{introduction-ecdar}) and therefore,
the system is required to react to input immediately. As a consequence,
there must also be a well defined reaction to input during the execution
of a task.

When an automaton is executing a task and it receives an input message
which it accepts, it may stop the currently executed task and proceed
as originally defined in ECDAR (i.e. traverse the corresponding edge),
if and only if the task is preemptive. Otherwise, the given input
will be ignored and the execution of the task continues.

To determine if a task is preemptive is up to the designer of the
system to decide. By default all tasks are non-preemptive.

\subsection{The ECDAR Framework}
\label{implementation-framework}

\input{32framework.tex}


\subsection{Synchronization}
\label{subsec:synch}

In the framework implementation, the Java keyword \textit{synchronized} is 
used for making certain operations quasi-atomic. That means, that a set of
instructions may not be interrupted by the execution of another thread -- 
i.e. traversals over edges.

This is mainly used for the logging of signals, so that logging time
is preserved and the output appears in the right order. \textit{Synchronized}
is also used, to set some internal states on TIOA, where the internal state
consists of multiple values that need to be set at the same time.

\textit{Synchronized} is furthermore used to prioritize handling of input.  The
method on the controller object, that is handling the signal, as well as those
on the TIOA that react to a signal if it is accepted, are modified with
\textit{synchronized}. This ensures that, before everything else, the input is
processed.


\subsection{Code Generation}
\label{implementation-code-generation}

\input{34generation.tex}
